Are kelp forests different? A comparison of kelp forests between contrasting study sites

### 2018-07-13 paper_draft.Rmd
doodle...

```{r global_options, include = FALSE}
knitr::opts_chunk$set(include = TRUE, echo = FALSE, warning = FALSE,
                      message = FALSE, tidy = FALSE, cache = FALSE,
                      fig.align = 'center',
                      fig.show = 'hold', fig.path = 'figures/deeper-')
```

@@

flora_df <- read.csv(file = "data/flora.csv", check.names = FALSE)
fauna_df <- read.csv(file = "data/fauna.csv", check.names = FALSE)
benthic <- read.csv(file = "data/benthic.csv", check.names = FALSE)
cover_df <- read.csv(file = "data/cover.csv", check.names = FALSE)
kelp_df <- read.csv(file = "data/kelp.csv", check.names = FALSE)

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x=id, y=species, colour = site, size =biomass)) +                   geom_point() + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'grey')) +
              ylab("Species") + 
              xlab("ID")

ggsave("figures/fig1.png", grid.arrange(plot_flora, plot_fauna))
grid.arrange(plot_flora, plot_fauna, ncol=1)
```

>>>>

```{r global_options, include = FALSE}
knitr::opts_chunk$set(include = TRUE, echo = FALSE, warning = FALSE,
                      message = FALSE, tidy = FALSE, cache = FALSE,
                      fig.align = 'center',
                      fig.show = 'hold', fig.path = 'figures/')
```

@@

flora_df <- read.csv(file = "data/flora.csv", check.names = FALSE)
fauna_df <- read.csv(file = "data/fauna.csv", check.names = FALSE)
benthic <- read.csv(file = "data/benthic.csv", check.names = FALSE)
cover_df <- read.csv(file = "data/cover.csv", check.names = FALSE)
kelp_df <- read.csv(file = "data/kelp.csv", check.names = FALSE)
urchin_df <- fauna_df[ , 28]

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x=site, y=biomass, colour = species)) +                             stat_summary(geom = "pointrange", data = fauna_lng) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'grey', colour = 'grey')) +
              ylab("") + 
              xlab("") +
              coord_flip()
grid.arrange(plot_flora, plot_fauna)

```
+ stat_summary(fun.y="sum", geom="point")
levels(droplevels(subdf$letters))
